Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-03-05 manuscript.tex
Correctly list extracted slices [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/632ef68b99eee4f636adf9fa43a9d6d5870ca4cb.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/632ef68b99eee4f636adf9fa43a9d6d5870ca4cb/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/624019174

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...4802042a90ffd281b24bc64e9bc89d2038405449}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/4802042a90ffd281b24bc64e9bc89d2038405449/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/4802042a90ffd281b24bc64e9bc89d2038405449}{habi/zmk-tooth-cohort-method-manuscript@4802042}
on March 5, 2021.

@@

\begin{figure}
\hypertarget{fig:extractedslices}{%
\centering
\includegraphics{images/Tooth036.ExtractedSlices.png}
\caption{Slice extraction for characterization of a tooth.
This tooth features a 1-1-1/1 root canal configuration as defined by Briseño et al.~{[}\protect\hyperlink{ref-ZTgDEakx}{17}{]}.
The blue line in the two leftmost panels shows the gray value plot along the longest tooth axis, the orange line shows the smoothed plot.
Based on the largest derivation we detect the enamel-dentin border at slice 1116 of this dataset.
Based on the bottom around slice 2839 we extracted the equidistant slices in-between.}\label{fig:extractedslices}
}
\end{figure}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...632ef68b99eee4f636adf9fa43a9d6d5870ca4cb}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/632ef68b99eee4f636adf9fa43a9d6d5870ca4cb/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/632ef68b99eee4f636adf9fa43a9d6d5870ca4cb}{habi/zmk-tooth-cohort-method-manuscript@632ef68}
on March 5, 2021.

@@

\begin{figure}
\hypertarget{fig:extractedslices}{%
\centering
\includegraphics{images/Tooth036.ExtractedSlices.png}
\caption{Slice extraction for characterization of a tooth.
This tooth features a 1-1-1/1 root canal configuration as defined by Briseño et al.~{[}\protect\hyperlink{ref-ZTgDEakx}{17}{]}.
The blue line in the two leftmost panels shows the gray value plot along the longest tooth axis, the orange line shows the smoothed plot.
Based on the largest derivation we detect the enamel-dentin border at slice 911 of this dataset.
Based on the bottom around slice 2341 we extracted the equidistant slices in-between.}\label{fig:extractedslices}
}
\end{figure}
